\chapter{Background}

Computer Vision can be thought of as a domain specific type of Signal Processing.  Any signal processing application can be viewed as a pipeline made of the following emements:

The sensing element:  A sensor is a device capable transforming the signal being sensed from the physical to the digital domain.

The filter Element:  The filter reduces load on the system by discarding less important information from the sensor

The detector element:  This element takes in the filtered signal and uses it determine the presence of a desired trait.

The work here focuses mainly on the detection part 


In our specific case the sensing element represents the array of pixels which represent our image.

We use several levels of filters to reduce the amount of data in our image to a managable level.  A more detailed description of the filters can be seen here.

From the filtered data we make a classification decision regarding certain aspects of our image.

A trainable classifier is a mathematical or algorithmic model can be used to make predictions on data not seen before based on data seen in the past.

Classifiers are used in a variety of areas like recommender systems, such as Netflix, to weather forcasting, to image recognition.

In order for these classifiers to perform well there must be a sufficiently large representative sample of data availiable to train the classifier.


The largest most comprehensive dataset of Anchient Chinese Calligraphy is the CADAL Dataset.

Since many of the characters present in the CADAL dataset are similar in nature the the Characters in the Collected Characters Stelle I 

For 
